\noindent {\huge \textbf{Andrea's Penne \& Cheese}} \hfill {\large \textbf{1 hour}}

% Ingredients
\vspace{15pt} \hrule \vspace{15pt}
\noindent {\LARGE \textbf{Ingredients}}
\begin{itemize}
	\item 2 tsp salt (\textit{definitely more})
	\item 1 lb penne pasta
	\item 2 cups whole milk
	\item 1 cup heavy cream
	\item $\frac{1}{4}$ cups unsalted butter
	\item $\frac{1}{4}$ cups flour
	\item 3 cups extra sharp cheddar
	\item 1 cup pepper jack
	\item 1 cup Gouda cheese
	\item 4 oz can of chile peppers
	\item $\frac{2}{3}$ cup sour cream
	\item 1 tsp cracked black pepper
	\item 2 tsp dry mustard
	\item $\frac{1}{2}$ tsp ground nutmeg
	\item 2 tsp Worcestershire sauce
	\item 2 tbsp cayenne pepper
\end{itemize}

% Directions
\vspace{15pt} \hrule \vspace{15pt}
\noindent {\LARGE \textbf{Directions}}
\begin{enumerate}
	\item Boil pasta \textit{al dente} in large pot of heavily salted water.
	\item In a sauce pan: heat milk and cream until thickened. Do not boil. \textit{This takes some time. Wait a few minutes before moving on to the next step.}
	\item In a large skillet: melt butter on medium heat.
	\item Sprinkle flour into skillet while whisking.
	\item Add the warmed milk and cream to the skillet.
	\item Add half of the cheese while whisking until smooth.
	\item Add sour cream and whisk until smooth.
	\item Add dry mustard, black pepper, cayenne, and ground nutmeg.
	\item Add Worcestershire sauce, chile peppers, and salt to taste.
	\item Combine pasta and sauce in a 9x13 in. baking dish and stir until uniform.
	\item Add remaining cheese to the top of the saucy pasta.
	\item Bake for \textbf{25 minutes} at \textbf{400 F} \textit{or until golden brown.}
\end{enumerate}
